---
title: "any() vs. all()"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A classmate recently asked me what the difference is between the `any()` and `all()` functions in R. This is a quick demo for how they work! 

Both `any()` and `all()` are functions that accept boolean vectors and return a single boolean value. 

`any()` will check to see if any single one of the values in the vector is `TRUE` - if so, it will return `TRUE`. 

```{r}
my_values <- c(1, 2, 3, 4, 5)

#This will be TRUE for the value 4, and thus will return TRUE overall
any(my_values == 4)
```

By comparison, `all()` will check if every single one of the values in the input vector is `TRUE` - if so, it will return `TRUE` (and otherwise will return `FALSE`). 

```{r}
my_values <- c(1, 2, 3, 4, 5)

#This will be TRUE for the value 4, but will be FALSE everywhere else. So we get FALSE overall...
all(my_values == 4)
```

```{r}
#This will be TRUE for all values in my_values, and thus will be TRUE overall. 
all(my_values > 0)
```

Both of these functions can be useful for boolean operations so that you don't have to 
abuse many `&` or `|` statements. Fantastic! 
